On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-05-10 TTau_Halpha/astro-ph/kurosawa.tex
After accepeted by MNRAS
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@717 25464f21-6099-402c-b30a-640f1d40d38b

We adopt the MA flow model of \citet*{hartmann:1994},
as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
in which the gas accretion on to the stellar surface from the innermost
part of the accretion disc occurs through a dipolar stellar magnetic
field. The magnetic field is assumed to be so strong that the gas
flow does not affect the underlying magnetic field itself. As shown
in Fig.~\ref{fig:config_discwind} (region~2), the innermost radius ($R_{\mathrm{mi}}$)
of the magnetosphere at the equatorial plane ($z=0$) is assigned
to be same as the inner radius ($R_{\mathrm{di}}$) of the accretion
disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
the equatorial plane) are set to be $2.2\, R_{*}$ and $3.0\, R_{*}$
respectively. The geometry of the magnetic field/stream
lines is fixed for all calculations. We note that this magnetospheric geometry
is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.

@@

The temperature structure of the magnetospheric used by
\citet{hartmann:1994} is adopted here. They computed the temperature,
assuming a volumetric heating rate which is proportional to $r^{-3}$,
by solving the energy balance of the radiative cooling rate of
\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
\citet{martin:1996} presented a self-consistent determination of the
thermal structure of the inflowing gas along the dipole magnetic field
(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
rate equations for hydrogen. He found that main heat source is
adiabatic compression due to the converging nature of the flow, and
the major contributors to the cooling process are bremsstrahlung
radiation and line emission from Ca~II and Mg~II ions. 
\citet*{muzerolle:1998} found that the line profile models computed
according to the temperature structure of \citet{martin:1996} do not
agree with observations, unlike profiles based on the (less
self-consistent) \citet{hartmann:1994} temperature distribution.  It
is clear that the temperature structure of the magnetosphere is still
a large source of uncertainty in the accretion model; here we adopted
the model of \citet{hartmann:1994}.

@@

The disc density distribution is given by 
\begin{equation}
  \rho_{\mathrm{d}}\left(w,z\right) = 
  \Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}
  \label{eq:disc-density-function}
\end{equation}
where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance
from the symmetry axis, the scale height, the distance from the disc
plane, and the surface density at the mid-plane, respectively. The
mid-plane surface density and the scale height are given as:
\begin{equation}
  \Sigma\left(w\right) = 
  \frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}
  \label{eq:density-midplane}
\end{equation} 
where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
and the disc mass respectively.
\begin{equation}
  h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.
  \label{eq:scale-height}
\end{equation}
With these parameters, the disc is slightly flared. The inner radius
of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc
mass, $M_{\mathrm{d}}$, is assumed to be 1/100 of the stellar mass
($M_{*}$), and the outer disc radius ($R_{\mathrm{di}}$) is
100~au. The velocity of the gas/dust in the disc is assumed to be
Keplerian.

@@

The dependency of the line profile on inclination angle ($i$) is
demonstrated in Fig.~\ref{fig:acc_inclination_effect}. The model
has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$).  The
figure shows that the peak (normalised) flux decreases as the
inclination angle increases, as does the EW.  
The line flux and the EWs decrease mainly because (1)~the fraction of
the accretion stream blocked by the photosphere increases as the
inclination increases (c.f.~Fig.~\ref{fig:config_discwind}, lower-left
part of the accretion stream i.e.~$z<0$ and $x<0$), and (2)~the
fraction of the accretion stream blocked by the inner part of the
accretion disc increases as the inclination increases
(c.f.~Fig.~\ref{fig:config_discwind}, lower-right part of accretion
stream i.e.~$z<0$ and $x>0$). While the photosphere mostly blocks the
blue-shifted part of the stream, the inner disc blocks the red-shifted
part.
The line EW in Fig.~\ref{fig:acc_inclination_effect} changes from
32 to 21\,\AA\, as the inclination changes from $10^\circ$ to
$80^\circ$, i.e.~a fractional change of 0.65.  On the other hand,
the 10~per~cent width of the line changes from 290 to
470~$\kmps$; hence, the fractional change is 1.6.  
A similar EW dependence on
inclination angle is found for the models with different 
magnetospheric temperatures and the mass-accretion rates.

@@

\citet{blandford:1982} showed that in order to launch a wind from a
disc plane magneto-centrifugally, the launching angle ($\theta_{L}$,
measured from the equatorial disc plane) must be less than $60^{\circ}$.
 In our models, the wind launching zone is restricted in
between $R_{\mathrm{wi}} < w_{i} < R_{\mathrm{wo}}$ (see
Fig.~\ref{fig:config_discwind} and Table~\ref{tab:std_parameters}) with
$R_{\mathrm{wi}} = 3\,R_{*} $ and 
$R_{\mathrm{wo}}=1$~au.  This sets the upper limit of the source displacement
distance ($d$) to be around $5.2\,R_{*}$ if we want to satisfy the
launching angle condition of \citet{blandford:1982} for all the
stream lines in our disc wind model.  In the models presented in
Fig.~\ref{fig:atlas_discwind_only} (and later in
Fig.~\ref{fig:atlas_hybrid} in next section), we have adopted 
$d =22\, R_{*}$ instead. This means that some part of the disc
wind ($3\,R_{*} < w_{i} < 25.4\,R_{*}$) may not be able to be launched
from the disc plane according to the model of \citet{blandford:1982}.
We have used a larger launching angle or a larger source displacement
distance for the following two reasons.

@@

Second, the larger source displacement model would provide a greater
consistency with the fraction of H$\alpha$ profiles affected by wind
absorption seen in observations.  According to the observations of
\citet{reipurth:1996} and \citet{alencar:2000}, more than 50 per cent
of CTTS show wind absorption features in their H$\alpha$
profiles. In our model, if the launching angle is too small
($\theta_{\mathrm{L}}<60^{\circ}$), the wind absorption feature would not be seen or
would be very small for profiles computed with $i<60^{\circ}$, as
demonstrated in Fig.~\ref{fig:discwind_d_effect}.  The situation will
however change if the field/stream line is not straight and bending
towards the symmetry axis as the wind travel higher above the disc.

In addition to the models given in Figs.~\ref{fig:atlas_discwind_only}
and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
R_{*}$ (not shown here) which satisfies the wind launching condition
of \citet{blandford:1982} in all parts of the disc wind zone in our
model.  These models showed that the wind absorption and emission
features weaken, but overall morphology dependence of the profiles on
the wind temperature and the wind acceleration rate is similar to
what we found in the models shown in
Figs.~\ref{fig:atlas_discwind_only} and \ref{fig:atlas_hybrid}.  The
minimum inclination angle at which the wind absorption becomes
important is larger than that of the models with a larger source
displacement ($d = 22\, R_{*}$) as expected.

@@

\citet{reipurth:1996} proposed a two-dimensional classification
of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
stars. Their classification scheme contains four classes (I, II, III
and IV) differentiated by the ratio of the secondary-to-primary emission
components in the profiles. Each class is divided into two sub-classes
(B and R) which depends whether the secondary peak is on the
blue or red side of the primary peak. Readers are referred to Fig.~4 of their paper.
Fig.~\ref{fig:atlas_reipurth} shows  sample model profiles
which are classified according to the definition of \citet{reipurth:1996}.
The combination of the disc wind, magnetospheric accretion flow, and
the accretion disc can reproduce all the classes of the profiles
seen in observations. The corresponding parameters of the
disc-wind-magnetosphere hybrid model used to reproduce the profiles
in the figure are summarised in Table~\ref{tab:classification} along
with brief comments on possible physical conditions which lead to
the profiles in each class. Below we discuss the Reipurth scheme in the
context of our models parameters. Readers are referred to
Appendix~\ref{sec:appendix} for the complete model profiles used in 
this discussion.          
Although in general H$\alpha$ in the spectra of CTTS shows a
significant amount of variablity, which may in some cases induced by
the rotational motion of an inclined magnetosphere
(e.g.~\citealt{johns:1995}; \citealt{bouvier:2003}), we restrict our
discussion in this section to the axi-symmetric case only.

@@

  \caption{The dependence of the H$\alpha$ model profiles on the
    inclination angle. The profiles computed at $i=10^{\circ}$ (solid
    line), $55^{\circ}$ (dotted line) and $80^{\circ}$ (dashed line)
    using (1)~the disc-wind-magnetosphere hybrid model (left;
    c.f. Section~\ref{sub:result-discwind-knigge}) and (2)~the disc,
    stellar wind, magnetosphere hybrid model (right panel;
    c.f. Fig.~\ref{fig:config_stellarwind}).  The parameters used for
    the magnetosphere are same for the both models,
    i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
    $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
    isothermal wind temperature and the wind acceleration parameter
    used in (1) are $T_{\mathrm{wind}}=7000~\mathrm{K}$ and
    $\beta=1.0$, and those in (2) are
    $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
    The wind mass-loss rates used in both models is
    $\dot{M}_{\mathrm{wind}}=10^{-8}~\mathrm{M_{\sun}~yr^{-1}}$ . 
    All the other parameters are same as in
    Sections~\ref{sub:result-discwind-hybrid} and
    \ref{sub:result-discwind-knigge}.  }

@@

We thank an anonymous referee who provided us valuable comments and
suggestions which improved the clarity of the manuscript. This work
was supported by PPARC standard grant PPA/G/S/2001/00081 and PPARC
rolling grant PP/C501609/1.

@@

Here we present our H$\alpha$ model line profile grid 
computed using the disc-wind-magnetosphere hybrid model
 in Section~\ref{sub:result-discwind-hybrid}.  All
the models use the reference parameters for the 
magnetospheric geometry and the photosphere as given in
Table~\ref{tab:std_parameters} in the main text. The ratio ($\mu$) of the
mass-loss rate to mass-accretion rate is fixed to 0.1 for  all the 
models. Three sets of model profiles, each with a different
mass-accretion rate, are presented here: 
(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas01}), 
(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas02}), and
(3) $\dot{M}_{\mathrm{acc}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$
(Fig.~\ref{fig:atlas02}).   The temperatures of the magnetospheres
used for (1), (2) and (3) are $7500\,\Kelvin$, $8500\,\Kelvin$ and
$9500\,\Kelvin$ respectively. The profiles are presented for the
inclination angles of $10^\circ$, $55^\circ$, and $80^\circ$. 
The disc-wind geometry used to compute these profiles are the same as in
Section~\ref{sub:result-discwind-hybrid}. These profiles are available
electrically at \url{http://www.astro.ex.ac.uk/people/rk/profiles}.

>>>>

We adopt the MA flow model of \citet*{hartmann:1994},
as done  by \citet{muzerolle:2001} and by \citet*{symington:2005},
in which the gas accretion on to the stellar surface from the innermost
part of the accretion disc occurs through a dipolar stellar magnetic
field. The magnetic field is assumed to be so strong that the gas
flow does not affect the underlying magnetic field itself. As shown
in Fig.~\ref{fig:config_discwind} (region~2), the innermost radius ($R_{\mathrm{mi}}$)
of the magnetosphere at the equatorial plane ($z=0$) is assigned
to be the same as the inner radius ($R_{\mathrm{di}}$) of the accretion
disc where the flow is truncated. In our models, $R_{\mathrm{mi}}$
and the outer radius ($R_{\mathrm{mo}}$) of the magnetosphere (at
the equatorial plane) are set to be $2.2\, R_{*}$ and $3.0\, R_{*}$
respectively. The geometry of the magnetic field/stream
lines is fixed for all calculations. We note that this magnetospheric geometry
is identical to the {}``small/wide'' model of \citet{muzerolle:2001}.

@@

The temperature structure of the magnetosphere used by
\citet{hartmann:1994} is adopted here. They computed the temperature,
assuming a volumetric heating rate which is proportional to $r^{-3}$,
by solving the energy balance of the radiative cooling rate of
\citet{hartmann:1982} and the heating rate \citep{hartmann:1994}.
\citet{martin:1996} presented a self-consistent determination of the
thermal structure of the inflowing gas along the dipole magnetic field
(equation~\ref{eq:dipole}) by solving the heat equation coupled to the
rate equations for hydrogen. He found that main heat source is
adiabatic compression due to the converging nature of the flow, and
the major contributors to the cooling process are bremsstrahlung
radiation and line emission from Ca~II and Mg~II ions. 
\citet*{muzerolle:1998} found that the line profile models computed
according to the temperature structure of \citet{martin:1996} do not
agree with observations, unlike profiles based on the (less
self-consistent) \citet{hartmann:1994} temperature distribution.  It
is clear that the temperature structure of the magnetosphere is still
a large source of uncertainty in the accretion model; here we adopted
the model of \citet{hartmann:1994}.

@@

The disc density distribution is given by 
\begin{equation}
  \rho_{\mathrm{d}}\left(w,z\right) = 
  \Sigma\left(w\right)\,\frac{1}{\sqrt{2\pi}h\left(w\right)}e^{-\left(\frac{z}{2h\left(w\right)}\right)^{2}}
  \label{eq:disc-density-function}
\end{equation}
where $w=\sqrt{x^{2}+y^{2}}$, $h$, $z$ and $\Sigma$ are the distance
from the symmetry axis, the scale height, the distance from the disc
plane, and the surface density at the mid-plane, respectively. The
mid-plane surface density and the scale height are given as:
\begin{equation}
  \Sigma\left(w\right) = 
  \frac{5M_{\mathrm{d}}}{8\pi R_{\mathrm{do}}^{2}}\, w^{-3/4}
  \label{eq:density-midplane}
\end{equation} 
where $R_{\mathrm{do}}$ and $M_{\mathrm{d}}$ are the disc radius
and the disc mass respectively, and
\begin{equation}
  h\left(w\right)=0.05\, R_{\mathrm{do}}\, w^{9/8}\,.
  \label{eq:scale-height}
\end{equation}
With these parameters, the disc is slightly flared. The inner radius
of the disc is set to $R_{\mathrm{di}}=R_{\mathrm{mi}}$ . The disc
mass, $M_{\mathrm{d}}$, is assumed to be 1/100 of the stellar mass
($M_{*}$), and the outer disc radius ($R_{\mathrm{do}}$) is
100~au. The velocity of the gas/dust in the disc is assumed to be
Keplerian.

@@

The dependency of the line profile on inclination angle ($i$) is
demonstrated in Fig.~\ref{fig:acc_inclination_effect}. The model
has  $T_{\mathrm{max}}=7500\,\mathrm{K}$ and
$\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$.  The
figure shows that the peak (normalised) flux decreases as the
inclination angle increases, as does the EW.  
The line flux and the EWs decrease mainly because (1)~the fraction of
the accretion stream blocked by the photosphere increases as the
inclination increases (c.f.~Fig.~\ref{fig:config_discwind}, lower-left
part of the accretion stream i.e.~$z<0$ and $x<0$), and (2)~the
fraction of the accretion stream blocked by the inner part of the
accretion disc increases as the inclination increases
(c.f.~Fig.~\ref{fig:config_discwind}, lower-right part of accretion
stream i.e.~$z<0$ and $x>0$). While the photosphere mostly blocks the
blue-shifted part of the stream, the inner disc blocks the red-shifted
part.
The line EW in Fig.~\ref{fig:acc_inclination_effect} changes from
32 to 21\,\AA\, as the inclination changes from $10^\circ$ to
$80^\circ$, i.e.~a fractional change of 0.65.  On the other hand,
the 10~per~cent width of the line changes from 290 to
470~$\kmps$; hence, the fractional change is 1.6.  
A similar EW dependence on
inclination angle is found for the models with different 
magnetospheric temperatures and the mass-accretion rates.

@@

\citet{blandford:1982} showed that in order to launch a wind from a
disc plane magneto-centrifugally, the launching angle ($\theta_{L}$,
measured from the equatorial disc plane) must be less than $60^{\circ}$.
 In our models, the wind launching zone is restricted in
between $R_{\mathrm{wi}} < w_{i} < R_{\mathrm{wo}}$ (see
Fig.~\ref{fig:config_discwind} and Table~\ref{tab:std_parameters}) with
$R_{\mathrm{wi}} = 3\,R_{*} $ and 
$R_{\mathrm{wo}}=1$~au.  This sets the upper limit of the source displacement
distance ($d$) to be around $5.2\,R_{*}$ if we want to satisfy the
launching angle condition of \citet{blandford:1982} for all the
stream lines in our disc wind model.  In the models presented in
Fig.~\ref{fig:atlas_discwind_only} (and later in
Fig.~\ref{fig:atlas_hybrid} in next section), we have adopted 
$d =22\, R_{*}$ instead. This means that some part of the disc
wind ($3\,R_{*} < w_{i} < 12.7\,R_{*}$) may not be able to be launched
from the disc plane according to the model of \citet{blandford:1982}.
We have used a larger launching angle or a larger source displacement
distance for the following two reasons.

@@

Second, the larger source displacement model would provide a greater
consistency with the fraction of H$\alpha$ profiles affected by wind
absorption seen in observations.  According to the observations of
\citet{reipurth:1996} and \citet{alencar:2000}, more than 50 per cent
of CTTS show wind absorption features in their H$\alpha$
profiles. In our model, if the launching angle is too small
($\theta_{\mathrm{L}}<60^{\circ}$), the wind absorption feature would not be seen or
would be very small for profiles computed with $i<60^{\circ}$, as
demonstrated in Fig.~\ref{fig:discwind_d_effect}.  The situation will
however change if the field/stream line is not straight and bending
towards the symmetry axis as the wind travels higher above the disc.

In addition to the models given in Figs.~\ref{fig:atlas_discwind_only}
and \ref{fig:atlas_hybrid}, we have computed the models with $d = 5\,
R_{*}$ (not shown here) which satisfy the wind launching condition
of \citet{blandford:1982} in all parts of the disc wind zone in our
model.  These models showed that the wind absorption and emission
features weaken, but overall morphology dependence of the profiles on
the wind temperature and the wind acceleration rate is similar to
what we found in the models shown in
Figs.~\ref{fig:atlas_discwind_only} and \ref{fig:atlas_hybrid}.  The
minimum inclination angle at which the wind absorption becomes
important is larger than that of the models with a larger source
displacement ($d = 22\, R_{*}$) as expected.

@@

\citet{reipurth:1996} proposed a two-dimensional classification
of H$\alpha$ emission profiles of T~Tauri stars and Herbig Ae/Be
stars. Their classification scheme contains four classes (I, II, III
and IV) differentiated by the ratio of the secondary-to-primary emission
components in the profiles. Each class is divided into two sub-classes
(B and R) which depends whether the secondary peak is on the
blue or red side of the primary peak. Readers are referred to Fig.~4 of their paper.
Fig.~\ref{fig:atlas_reipurth} shows  sample model profiles
which are classified according to the definition of \citet{reipurth:1996}.
The combination of the disc wind, magnetospheric accretion flow, and
the accretion disc can reproduce all the classes of the profiles
seen in observations. The corresponding parameters of the
disc-wind-magnetosphere hybrid model used to reproduce the profiles
in the figure are summarised in Table~\ref{tab:classification} along
with brief comments on possible physical conditions which lead to
the profiles in each class. Below we discuss the Reipurth scheme in the
context of our models parameters. Readers are referred to
Appendix~\ref{sec:appendix} for the complete model profiles used in 
this discussion.          
Although in general H$\alpha$ in the spectra of CTTS shows a
significant amount of variablity, which may in some cases be induced by
the rotational motion of an inclined magnetosphere
(e.g.~\citealt{johns:1995}; \citealt{bouvier:2003}), we restrict our
discussion in this section to the axi-symmetric case only.

@@

  \caption{The dependence of the H$\alpha$ model profiles on the
    inclination angle. The profiles computed at $i=10^{\circ}$ (solid
    line), $55^{\circ}$ (dotted line) and $80^{\circ}$ (dashed line)
    using (1)~the disc-wind-magnetosphere hybrid model (left;
    c.f. Section~\ref{sub:result-discwind-knigge}) and (2)~the disc,
    stellar wind, magnetosphere hybrid model (right panel;
    c.f. Fig.~\ref{fig:config_stellarwind}).  The parameters used for
    the magnetosphere are same for the both models,
    i.e. $T_{\mathrm{max}}=7500~\mathrm{K}$ and
    $\dot{M}_{\mathrm{acc}}=10^{-7}~\mathrm{M_{\sun}~yr^{-1}}$.  The
    isothermal wind temperature and the wind acceleration parameter
    used in (1) are $T_{\mathrm{wind}}=7000~\mathrm{K}$ and
    $\beta=1.0$, and those in (2) are
    $T_{\mathrm{wind}}=9000~\mathrm{K}$ and $\beta=1.0$ respectively.
    The wind mass-loss rate used in both models is
    $\dot{M}_{\mathrm{wind}}=10^{-8}~\mathrm{M_{\sun}~yr^{-1}}$ . 
    All the other parameters are same as in
    Sections~\ref{sub:result-discwind-hybrid} and
    \ref{sub:result-discwind-knigge}.  }

@@

We thank the referee, Silvia Alencar, who provided us with valuable comments and
suggestions which improved the clarity of the manuscript. This work
was supported by PPARC standard grant PPA/G/S/2001/00081 and PPARC
rolling grant PP/C501609/1.

@@

Here we present our H$\alpha$ model line profile grid 
computed using the disc-wind-magnetosphere hybrid model
 in Section~\ref{sub:result-discwind-hybrid}.  All
the models use the reference parameters for the 
magnetospheric geometry and the photosphere as given in
Table~\ref{tab:std_parameters} in the main text. The ratio ($\mu$) of the
mass-loss rate to mass-accretion rate is fixed to 0.1 for  all the 
models. Three sets of model profiles, each with a different
mass-accretion rate, are presented here: 
(1) $\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas01}), 
(2) $\dot{M}_{\mathrm{acc}}=10^{-8}\,\mathrm{M_{\sun}\,yr^{-1}}$ (Fig.~\ref{fig:atlas02}), and
(3) $\dot{M}_{\mathrm{acc}}=10^{-9}\,\mathrm{M_{\sun}\,yr^{-1}}$
(Fig.~\ref{fig:atlas03}).   The temperatures of the magnetospheres
used for (1), (2) and (3) are $7500\,\Kelvin$, $8500\,\Kelvin$ and
$9500\,\Kelvin$ respectively. The profiles are presented for the
inclination angles of $10^\circ$, $55^\circ$, and $80^\circ$. 
The disc-wind geometry used to compute these profiles are the same as in
Section~\ref{sub:result-discwind-hybrid}. These profiles are available
electrically at \url{http://www.astro.ex.ac.uk/people/rk/profiles}.
